Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-28 pnas/Towards.tex
Finished modifications in the appendix

The micrographs for the experiment presented in Figures~\ref{fig:cryo_detection} \revised{and~\ref{fig:cryo_noisy_micros_for_rec}} were generated as follows. We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}. %\cite{aspire}.
We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension. The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices. We continue adding projections to the micrograph until no more projections can be added without violating the separation condition. \revised{For the noise, we define signal-to-noise ratio slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise. The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs. We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.}

>>>>

The micrographs for the experiment presented in Figures~\ref{fig:cryo_detection} \revised{and~\ref{fig:cryo_noisy_micros_for_rec}} were generated as follows. We sample rotation matrices from SO(3) uniformly at random using the QR-based algorithm described in~\cite{stewart1980efficient}, and generate the projection of the volume corresponding to that rotation matrix using \verb|cryo_project| in ASPIRE\footnote{\url{http://spr.math.princeton.edu}}. %\cite{aspire}.
We keep track of the indices at which the upper left corner of a projection can be placed without violating the separation condition, so all projections are separated by at least 30 pixels in each dimension. The location of the upper left corner of each new projection is picked uniformly at random from the set of available indices. We continue adding projections to the micrograph until no more projections can be added without violating the separation condition. \revised{In the experiments, we define SNR slightly differently than in the toy model, namely as $\text{SNR} = \frac{\text{var}(\mathcal{I})}{\sigma^2}$ where $\text{var}(\mathcal{I})$ is the variance of our stack of micrographs and $\sigma^2$ is the variance of noise. The noise level in the noisy micrograph in Figure~\ref{fig:cryo_detection} was $\text{SNR} = 1/1024$, the noise level in Figure~\ref{fig:cryo_noisy_micros_for_rec} was $\text{SNR} = 1/16$ for the TRPV1 micrographs and $\text{SNR} = 1/64$ for the BPTI micrographs. We used 300 micrographs for each of the noisy reconstructions presented in Figure~\ref{fig:cryo_recon}.}
